Kronos \& Krios: TBD

### 2017-05-29 paper/ms.tex
Add reference for yonsei-yale isochrone
Remove individual system listings in intro

Independently, in efforts to connect the host star's chemistry to
its planetary system, wide binaries with similar or very different planetary architectures around
the component stars are particularly useful as chemical signatures related to planet formation or accretion
can be revealed in a differential sense without any regard to the Galactic chemical evolution
as long as we assume that the two stars should have been born together with identical composition.
For close-in giant planets, it has been established that the planet-metallicity relation
is primordial, and that the enhanced metallicity in giant planet-hosting stars likely
promoted the formation of giant planets (\citealt{Fischer:2005aa}) by increasing
the availability of small particle condensates that forms planetesimals.
On the other hand, if host stars are to be polluted after their birth
by rocky planetary material with high refractory-to-volatile ratio,
the convective envelope of the stars may be enhanced in refractory elements (e.g., \elem{Fe})
compared to their initial state.
Thus, differing planet formation or accretion in the two otherwise identical stars
may imprint a difference of chemical abundances that depends on the
condensation temperature (\Tcondens).
Several systems in which at least one star hosts at least one planet
have been studied so far with high resolution spectroscopy in this context
(\citealt{Teske:2013aa,Mack:2014aa,Liu:2014aa,Teske:2015aa,Saffe:2015aa,
  Ramirez:2015aa,Biazzo:2015aa,Mack:2016aa,Teske:2016aa,Teske:2016ab}).
The results and interpretations of these studies are varied:
while some systems (e.g., HAT-P-1 (\citealt{Liu:2014aa}),
HD~20782/1 (\citealt{Mack:2014aa}), HD~80606/7 (\citealt{Saffe:2015aa,Mack:2014aa});
see also \citealt{Desidera:2004aa,Gratton:2001aa})
found no difference, other studies (e.g., XO-2 (\citealt{Teske:2015aa,Ramirez:2015aa,Biazzo:2015aa}))
have found a \Tcondens-dependent difference in abundance.
The increasing difference of abundance with condensation temperature
has been attributed both to more yet-undiscovered rocky planets around
the relatively refractory-poor star and to late time accretion of
refractory-rich planetary material (\citealt{Ramirez:2015aa,Biazzo:2015aa}.
% maybe want to point out the former interpretation roots back to melendez+09
% and some doubt to that interpretation...

@@

The fact that the two stars share a very similar space motion
at a separation of $0.6$~pc strongly argues that the pair is coeval.
We consider other age indicators apart from their phase space coordinates
to assess the ages and coevality of the two stars.
First, given the precise measurements of $\log(g)$, $T_\mathrm{eff}$,
comparing these values to theoretical isochrones may also be indicative of the two stars' ages.
We perform isochrone fitting using the Yale-Yonsei model isocrones (\todo{CITE}).
The input data are $\log(g)$, $T_\mathrm{eff}$, \feh, parallaxes, $B$-band magnitudes, and their errors.
The isochrone ages of \sunanalog\ and \bizarreone\ are
$4.00_{-1.56}^{+1.51}$~Gyr and $4.28_{-1.03}^{+1.11}$~Gyr, respectively,
consistent with them being coeval.

>>>>

Independently, in efforts to connect the host star's chemistry to
its planetary system, wide binaries with similar or very different planetary architectures around
the component stars are particularly useful as chemical signatures related to planet formation or accretion
can be revealed in a differential sense without any regard to the Galactic chemical evolution
as long as we assume that the two stars should have been born together with identical composition.
For close-in giant planets, it has been established that the planet-metallicity relation
is primordial, and that the enhanced metallicity in giant planet-hosting stars likely
promoted the formation of giant planets (\citealt{Fischer:2005aa}) by increasing
the availability of small particle condensates that forms planetesimals.
On the other hand, if host stars are to be polluted after their birth
by rocky planetary material with high refractory-to-volatile ratio,
the convective envelope of the stars may be enhanced in refractory elements (e.g., \elem{Fe})
compared to their initial state.
Thus, differing planet formation or accretion in the two otherwise identical stars
may imprint a difference of chemical abundances that depends on the
condensation temperature (\Tcondens).
Several systems in which at least one star hosts at least one planet
have been studied so far with high resolution spectroscopy in this context
(\citealt{Teske:2013aa,Mack:2014aa,Liu:2014aa,Teske:2015aa,Saffe:2015aa,
  Ramirez:2015aa,Biazzo:2015aa,Mack:2016aa,Teske:2016aa,Teske:2016ab}).
The results and interpretations of these studies are varied: while some systems
found no difference (see also \citealt{Desidera:2004aa,Gratton:2001aa}), other
studies  have found a \Tcondens-dependent difference in abundance.
The increasing difference of abundance with condensation temperature
has been attributed both to more yet-undiscovered rocky planets around
the relatively refractory-poor star and to late time accretion of
refractory-rich planetary material (\citealt{Ramirez:2015aa,Biazzo:2015aa}.
% maybe want to point out the former interpretation roots back to melendez+09
% and some doubt to that interpretation...

@@

The fact that the two stars share a very similar space motion
at a separation of $0.6$~pc strongly argues that the pair is coeval.
We consider other age indicators apart from their phase space coordinates
to assess the ages and coevality of the two stars.
First, given the precise measurements of $\log(g)$, $T_\mathrm{eff}$,
comparing these values to theoretical isochrones may also be indicative of the two stars' ages.
We perform isochrone fitting using the Yale-Yonsei model isochrones (\citealt{2013ApJ...776...87S}).
The input data are $\log(g)$, $T_\mathrm{eff}$, \feh, parallaxes, $B$-band magnitudes, and their errors.
The isochrone ages of \sunanalog\ and \bizarreone\ are
$4.00_{-1.56}^{+1.51}$~Gyr and $4.28_{-1.03}^{+1.11}$~Gyr, respectively,
consistent with them being coeval.
